The Role of Shallow Processing in Agreement Attraction

### 2020-01-21 agremeent_draft_dec17/draft_dec17.Rnw
Number Check: 1 out of 4

@@

We recruited 118 undergraduate students to participate in Experiment 1 in exchange for course credit. All participants were native speakers of Turkish, with an average age of \Sexpr{round(mean(form_exp1$Age))} (range: \Sexpr{min(form_exp1$Age)} -- \Sexpr{max(form_exp1$Age)}). 
These items were not included in the analysis. Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm. 
%to-do: cite ibexfarm

@@

We used 40 sets of sentences like (\ref{item:exp1ExperimentalItems}), in which we manipulated 
(i) the number of the attractor noun, and
(ii) the number agreement on the verb. 
Plural number and plural agreement were both marked with the affix \textit{-ler/-lar}, while singular number and singular agreement were marked with its absence. 
%
All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun cassied possessive case. Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical.
% to-do: Didn't we use Lago's items as a base?? If so, we need to say this here, and also how much we've changed, and how much remained.
Unlike the \citet{LagoEtAl:2018} sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.

% to-do: This all needs to go up, to the description of the potential confound in Lago et al.'s study.
%This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative. 
The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
%
The pre-verbal adverbials preceding the verb in our experimental sentences consisted of 2-3 words (15 characters on average).

% to-do: Why are all sentences in aorist instead of past (as they are in the actual items)?
\ex. \label{item:exp1ExperimentalItems}
%
\a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-plpl}\\ 
  \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
  \glt \textit{`The cooks of the manager were jumping in the kitchen non-stop.'}
%
\b. \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{item:exp1expitem-plsg}\\ 
  \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
  \glt \textit{`The cooks of the manager was jumping in the kitchen non-stop.'}
%
\c. \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-sgpl}\\ 
  \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor-lar}.\\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
  \glt \textit{`The cook of the manager were jumping in the kitchen non-stop.'}
%
\d. \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp1expitem-sgsg}\\ 
  \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpl-ıyor}. \\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
  \glt \textit{`The cook of the manager was jumping in the kitchen non-stop.'}

We intermixed our experimental sentences with 40 filler sentences of two types, as illustrated in (\ref{item:exp1FillerItems}). To compensate for the fact that among experimental sentences, all ungrammatical sentences ended in a plural-agreeing verb, while all grammatical sentences ended in a singular-agreeing verb, we included 20 grammatical sentences with plural verbs, and 20 ungrammatical sentences with singular agreement. This was done in order to discourage participants from using a strategy based on verb number.

@@

\ex. \label{item:exp1FillerItems}
%
\a. \textsc{Grammatical Filler (Plural Verb)}\\ 
  \gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ 
  sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`When the sociologist's student talked, they exposed an inconsistency.'}
%to-do: Translation above doesn't make sense.
%
%
\b. \textsc{Ungrammatical Filler (Singular Verb)}\\ 
\gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}.\\ 
dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
\glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}
% to-do: Does the above mean that it's grammatical with another meaning?

@@

The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each experimental session took approximately XXX minutes to complete.
% to-do: How much time did it take?
%
Prior to the start of the experiment, participants provided demographic information, as well as informed consent to participate in the experiment. They read the instructions, and were given 9 practice trials before the experiment began.
%
Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentation of the sentence in the center of the screen, followed by an acceptability judgment. 
Sentences were presented word-by-word in 30pt font size, and at a rate of 400 ms per word. Participants pressed the key 'P' for \textit{'acceptable'} and 'Q' for \textit{'unacceptable'}. They were instructed to provide an acceptability rating before the 5,000 ms deadline. During the experiment, they were reminded to respond faster if they responded too slowly.

@@

We used the R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,]{GelmanHill:2007}. We analyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors. Moreover, we used by-participant and by-item intercepts and slopes for all predictors.

Data for experiment 1, along with our analysis scripts can be found \texttt{link hidden due to blind review}.
% to-do: Please create a repo where we can put all of this, or specify the github URL. I'm not aware of any blind reviews.

@@

We recruited 79 native speakers of Turkish to participate in Experiment 2. Their average age was \Sexpr{round(mean(form_exp2$Age))}, ranging from \Sexpr{min(form_exp2$Age)} to \Sexpr{max(form_exp2$Age)}.

Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?

@@

In Experiment 2, participants saw the sentences word by word in the middle of their screen. We have again formed 40 sets of items. The grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor (\textit{singular} x \textit{plural}) were manipulated. Unlike Experiment 1, we used nominalized relative clause attractors instead of nouns. We took advantage of syncretism between Turkish nominal and verbal plural marker. Both of these morphemes spells-out as \textit{-lAr}, which enables us to check whether agreement attraction in Turkish can be explained by an extremely shallow dependency parsing based on the forms of morphemes rather than linguistic features.

All experimental sentences followed the same template as the experiment one except for the nature of the attractor: \textit{RC-Bare Noun-Adverb-Verb}. 
We have used the same verbs, and have not changed the distribution of verb types. We also utilized the same or extremely similar adverbials in length. We again did not manipulate the number of the head noun and manipulated the number of the attractor. Relative clauses we used in this experiment are all object relative clauses and they are all marked with canonical \textit{-dIK} nominalizer. Since Turkish is a pro-drop language, we also dropped the subject within the embedded clause, thus ending up with a one-word object relative clause whose head is also the controller of the number agreement on the matrix verb. One example set of experimental items can be seen in \ref{item:exp2ExperimentalItems}.

\ex. \label{item:exp2ExperimentalItems}
%
\a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-plpl}\\ 
  \gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
%
\b. \textit{Plural Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-plsg}\\ 
  \gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
%
\c. \textit{Singular Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-sgpl}\\
  \gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
  hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
%
\d. \textit{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-sgsg}\\ 
  \gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
  hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}

In our filler items for Experiment 2, we made sure that every sentence starts with an object relative clause. We used plural distractors with grammatical verbs and singular distractors with ungrammatical verbs. In all of our filler sentences, the dependency between the first NP subject and its verb resolved in an adverbial embedded sentence. Grammatical filler items in Experiment 2 all had a template of
XXX
%\textit{RC$_{\textsc{pl}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{pl}}$}, 
whereas ungrammatical filler items used a template of 
XXX
%\textit{RC$_{\textsc{sg}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{sg}$}

Again, to avoid a possible strategy where participants use plural ending as a direct indication of ungrammaticality, half of our fillers were with an overt plural marking on a grammatical verb while the other half were without an overt plural marking on an ungrammatical verb. We used Turkish pro-drop characteristics which enable participants to form a dependency between the matrix verb and the null subject. Example filler sentences can be seen in \ref{item:exp2FillerItems}

\ex. \label{item:exp2FillerItems}
%
\a. \textit{Plural Grammatical Verb}\\ 
  \gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
  read-\textsc{caus}-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  student successful be-\textsc{nmlz} happy be-\textsc{pst}-\textsc{pl}.\\
  \glt `When the student they sponsored become successful, they became happy.' 
%
\b. \textit{Singular Ungrammatical Verb}\\ 
  \gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
  trick-\textsc{nmlz}-\textsc{poss}  man pay-\textsc{neg}-\textsc{nmlz} dish for.hours clean-\textsc{pst}.\\
  \glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'

\subsection{Procedure and Analysis} \label{sec:exp2:procedure_analysis}

@@

% to-do: some more details.
% In Experiment 2, the same procedure as Experiment 1 has been followed with regards to how sentences are presented within the experiment.

We analyzed the percentages of 'yes' answers given by the participants in experimental conditions. In the analysis of this experiment, we have included experimental items from our Experiments 1 and 2 to check the interaction between experiments and quantify the difference between verbal and nominal plural markers. In Experiment 2 as well, we excluded participants (\Sexpr{length(bad_subjects2)}) who had more than 0.25 points of difference in accuracy between grammatical conditions, which implicates that they did not give enough attention to all conditions. We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep{GelmanHill:2007}. We added our independent variables, i.e. grammaticality of the sentence and the overt number information on the distractors, and random variable experiment as a factor. Analyses by items and participants are also conducted as a 
part of the Bayesian hierarchical models. Data regarding our experiments and analysis can be found in \texttt{link hidden due to blind review}.

Across participants, a total \Sexpr{sum(is.na(df_exp2_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp2_na_nofillers$subject))} different participants. These items were not included in the analysis.

% Should I rephrase these parts?
%Prior the experiments, participant gave information regarding themselves and a consent to start to the experiment. They read the instructions where we showed what they will see in the experiment, what will be going to ask to participants, and where we informed them to be fast and accurate during the experiment. Every session started with practice session where participants have been informed being a bit faster when they were not. The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each word stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen. After the sentence is completed, participants were asked "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad. Apart from the practice items, we did not provide any feedback regarding their answer. However, participants were asked to be faster when they waited more than 5000 ms to answer the acceptability question.

@@

\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for both Experiment 1 and Experiment 2. We see that there is no effect resembling agreement attraction in the ungrammatical conditions of Experiment 2. Ungrammatical conditions showed comparable effects (\Sexpr{avg_exp2$resp$M[7]} and \Sexpr{avg_exp2$resp$M[8]} for plural and singular attractors respeectively) regardless of the attractor's number.

@@

The observations we made through \autoref{fig:exp2AvgResponse} also surfaces when we look at the estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp2ResponseModel}. As is visible from the figure, the model shows a negative three-way interaction between grammaticality, type of attractor (nominal vs. verbal), and attractor number, which entails a reduced effect of agreement attraction in Experiment 2 compared to Experiment 1.

@@

@@

>>>>

% to-do: This all needs to go up, to the description of the potential confound in Lago et al.'s study.
%This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative.

@@

We recruited 118 undergraduate students to participate in Experiment 1 in exchange for course credit. All participants were native speakers of Turkish, with an average age of \Sexpr{round(mean(form_exp1$Age))} (range: \Sexpr{min(form_exp1$Age)} -- \Sexpr{max(form_exp1$Age)}).  
Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University. All participants provided informed consent prior to their participation.

@@

We used 40 sets of sentences like (\ref{item:exp1ExperimentalItems}), in which we manipulated 
(i) the number of the attractor noun, and
(ii) the number agreement on the verb. 
Plural number and plural agreement were both marked with the affix \textit{-ler/-lar}, while singular number and singular agreement were marked with its absence. 
%
We have used the experimental items in \citet{LagoEtAl:2018} as a base. 
All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun carried possessive case. 
Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical. 
Moreover, as in the original study, the properties of the nouns in the complex subject NP and the relation between these nouns held constant in our replication. 
The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
Both in \citet{LagoEtAl:2018} and in our replication, pre-verbal adverbials consisting of 2-3 words (15 characters on average) are used.
Unlike the \citet{LagoEtAl:2018} sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.

\ex. \label{item:exp1ExperimentalItems}
%
\a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-plpl}\\ 
  \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`The cooks of the manager were jumping in the kitchen non-stop.'}
%
\b. \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{item:exp1expitem-plsg}\\ 
  \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
  \glt \textit{`The cooks of the manager was jumping in the kitchen non-stop.'}
%
\c. \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-sgpl}\\ 
  \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`The cook of the manager were jumping in the kitchen non-stop.'}
%
\d. \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp1expitem-sgsg}\\ 
  \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}. \\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
  \glt \textit{`The cook of the manager was jumping in the kitchen non-stop.'}

We intermixed our experimental sentences with 40 filler sentences of two types, as illustrated in (\ref{item:exp1FillerItems}). 
To compensate for the fact that among experimental sentences, all ungrammatical sentences ended in a plural-agreeing verb, while all grammatical sentences ended in a singular-agreeing verb, we included 20 grammatical sentences with plural verbs, and 20 ungrammatical sentences with singular agreement. 
This was done in order to discourage participants from using a strategy based on verb number. 
Filler items followed a similar template in which sentence again started with a complex genitive-possessive noun phrase. 
However, in filler items, they were the controller of an embedded clause which serves as a adverbial. 
In grammatical fillers, we have made use of pro-dropped subject strategy in Turkish; thus, it enabled us to use plural verb without having ungrammatical sentences as in (\ref{item:exp1GrammaticalFiller}). The object \textit{tutarsızlık} is a bare nominal preceding a light verb construction. 
Differently in ungrammatical fillers, bare nominal did not precede a light verb construction, but an adverb and a verb. Since Turkish only allows bare nominals right next to the verb, sentences were deemed ungrammatical when the participants read the verb.

@@

\ex. \label{item:exp1FillerItems}
%
\a. \label{item:exp1GrammaticalFiller} \textsc{Grammatical Filler (Plural Verb)}\\ 
  \gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ %utku: what does this bold mean? if it the dependency between them then the bold parts are not correct. ogrencisi is the subject of the verb konusunca, and the subject of the matrix verb cikardilar is omitted.
  sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`When the student of the sociologist spoke, they revealed an inconsistency.'}
%to-do: Translation above doesn't make sense.
%
%
\b. \textsc{Ungrammatical Filler (Singular Verb)}\\ 
\gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}.\\ 
dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
\glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}
% to-do: Does the above mean that it's grammatical with another meaning?

@@

The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each experimental session took approximately 25 minutes to complete.
%
Prior to the start of the experiment, participants provided demographic information, as well as informed consent to participate in the experiment. They read the instructions, and were given 9 practice trials before the experiment began.
%
Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentation of the sentence in the center of the screen, followed by an acceptability judgment. 
Sentences were presented word-by-word in 30pt font size, and at a rate of 400 ms per word. Between each word, participants saw a blank screen for 100 ms. Participants pressed the key 'P' for \textit{'acceptable'} and 'Q' for \textit{'unacceptable'}. They were instructed to provide an acceptability rating before the 5,000 ms deadline. During the experiment, they were reminded to respond faster if they responded too slowly.

@@

We used the R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,][]{GelmanHill:2007}. We analyzed only experimental sentences, and used 
(i) grammaticality of the sentence, 
(ii) attractor number, and 
(iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors. 
Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
Data for experiment 1, along with our analysis scripts can be found in \url{https://github.com/utkuturk/replication_lagoetal2018}.

@@

We recruited 79 undergraduate students to participate in Experiment 2 in exchange for course credit. All participants were native speakers of Turkish, with an average age of \Sexpr{round(mean(form_exp2$Age))} (range: \Sexpr{min(form_exp2$Age)} - \Sexpr{max(form_exp2$Age)}). 
Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University. All participants provided informed consent prior to their participation.

@@

We used 40 sets of sentences like
(\ref{item:exp2ExperimentalItems}), in which we manipulated
(i) the number of the attractor, and
(ii) the number agreement on the verb. 
Unlike Experiment 1, we used the verb of a nominalized relative clause (i.e. \textit{tuttukları}) as an attractor instead of a genitive marked noun. 
We took advantage of syncretism between Turkish nominal and verbal plural marker. Both of these morphemes spells-out as \textit{-lAr}, which enables us to check whether agreement attraction in Turkish can be explained by an extremely shallow dependency parsing based on the forms of morphemes rather than linguistic features.

All sentences started with a complex subject NP like \textit{`the cook that they hired'} (\textit{tuttukları aşçı}), in which the verb of the relative clause functioned as the attractor. Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical.  
We have used the same verbs, and have not changed the distribution of verb types. We also utilized the same or similar adverbials in length.
Relative clauses we used in this experiment are all object relative clauses, and they are all marked with canonical \textit{-dIK} nominalizer. Since Turkish is a pro-drop language, we also dropped the subject within the embedded clause, thus ending up with a one-word object relative clause whose head is the controller of the number agreement on the matrix verb. One example set of experimental items can be seen in \ref{item:exp2ExperimentalItems}.

\ex. \label{item:exp2ExperimentalItems}
%
\a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-plpl}\\ 
  \gll *[Tut-tuk-lar-ı \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
%
\b. \textsc{Plural Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-plsg}\\ 
  \gll [Tut-tuk-lar-ı \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı}.\\ 
  hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}
%
\c. \textsc{Singular Attractor, Ungrammatical (Plural Verb)}\label{item:exp2expitem-sgpl}\\
  \gll *[Tut-tuğ-u \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
  hire-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`The cook that they hired were jumping in the kitchen non-stop.'}
%
\d. \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp2expitem-sgsg}\\ 
  \gll [Tut-tuğ-u \textbf{aşcı}] mutfak-ta sürekli \textbf{zıpla-fı}.\\ 
  hire-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
  \glt \textit{`The cook that they hired was jumping in the kitchen non-stop.'}

In addition to the experimental items, we used 40 filler sentences of two types, both of which starts with an object relative clause, as illustrated in (\ref{item:exp2FillerItems}). Similar to Experiment 1, our filler items included 20 grammatical sentences with an overtly plural marked verbs, and 20 ungrammatical sentences with no overt plural marking, thus singular. 
This was done in order to discourage participants from using a strategy based on verb number. 
In all of our filler sentences, the dependency between the first complex NP subject modified with an object relative clause and its verb resolved in an adverbial embedded sentence. 
In grammatical fillers, we have used intransitive verbs with a pro-dropped subject as in (\ref{item:exp2FillerItems_plural}). 
In ungrammatical fillers, we created the ungrammaticality by placing an adverbial between the bare nominal object and the verb as in (\ref{item:exp2FillerItems_singular}).

\ex. \label{item:exp2FillerItems}
%
\a. \label{item:exp2FillerItems_plural} \textsc{Grammatical Filler (Plural Verb)}\\ 
  \gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
  read-\textsc{caus}-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  student successful be-\textsc{nmlz} happy be-\textsc{pst}-\textsc{pl}.\\
  \glt `When the student they sponsored become successful, they became happy.' 
%
\b. \label{item:exp2FillerItems_singular} \textit{Ungrammatical Filler (Singular Verb)}\\ 
  \gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
  trick-\textsc{nmlz}-\textsc{poss}  man pay-\textsc{neg}-\textsc{nmlz} dish for.hours clean-\textsc{pst}.\\
  \glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'

\subsection{Procedure} \label{sec:exp2:procedure}

The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). For each participant, experiment took approximately 25 minutes to complete.
Participants were asked to provide information regarding their native language and age. They were also asked for their consent to participate in the experiment.
Prior to experimental items, participants read the instructions, and were given 9 practice items with feedback on their accuracy.
Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentantion of the sentence in the center of the screen, followed by an acceptability judgment. Sentences were presented in 30pt font size, and at a rate of 400 ms per word. Between each word, participants saw a blank screen for 100 ms. Participants pressed the key `P' for `\textit{acceptable}' and `Q' for `\textit{unacceptable}'.
Within instructions, they were told to provide an acceptability rating before 5,000 ms deadline. During the experiment, they were reminded to respondfaster if they did not respond within 5,000 ms.

\subsection{Analysis} \label{sec:exp2:analysis}

@@

In our analysis, we used the items from Experiment 1, as well as the items from Experiment 2. this decision was made to answer our hypothesis that whether or not participants use the form of the plural suffix rather than the linguistic features. A presence of interaction between the attractor type (\textit{nominal} vs. \textit{verbal}) and the agreement attraction effect would indicate that people use the linguistic features rather than the form of the plural suffix.

Similar to Experiment 1, we removed the data for all participants who did not exceed the threshold of 25 percentage points in `yes' responses between the grammatical condition and the ungrammatical condition with singular attractors. As a result, we excluded \Sexpr{stopifnot(length(bad_subjects2) == 1)} one participant from the Experiment 2, and \Sexpr{length(bad_subjects)} participant from the Experiment 1.

We used R packages brms \citep{R-brms_b} and rstan \citep{R-stan} to fit Bayesian hierarchical models \citep[e.g.,][]{GelmanHill:2007}. We aalyzed only experimental sentences, and used (i) grammaticality of the sentence, (ii) attractor number, and (iii) type of the plural suffix (i.e., experiment), as well as their interactions as predictors. 
Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
Data for Experiment 2, along with our analysis scripts can be found in \url{https://github.com/utkuturk/orc-attractor_numberattraction}.

%Across participants, a total \Sexpr{sum(is.na(df_exp2_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp2_na_nofillers$subject))} different participants. These items were not included in the analysis.

@@

<<curEntries>>=

exp2_cur_entry1 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "ungrammatical", attractor_num == "plural")
exp2_cur_entry2 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "ungrammatical", attractor_num == "singular")

exp2_cur_entry3 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "grammatical", attractor_num == "singular")
exp2_cur_entry4 = avg_exp2$resp %>% filter(experiment == "Experiment 2", grammatical == "grammatical", attractor_num == "plural")

\autoref{fig:exp2AvgResponse} shows the average proportions of 'acceptable' responses by experimental conditions for Experiment 2. 
It shows that ungrammatical sentences with plural attractors are rated as acceptable 
(M = \Sexpr{exp2_cur_entry1$M}, 
SE = \Sexpr{exp2_cur_entry1$SE}) 
as their counterparts with singular attractors 
(M = \Sexpr{exp2_cur_entry2$M}, 
SE = \Sexpr{exp2_cur_entry2$SE}). The lack of effect (\Sexpr{sprintf("%0.2f", exp2_cur_entry1$M-exp2_cur_entry2$M)}) compared to the magnitude of the effect in Experiment 1 (\Sexpr{sprintf("%0.2f", cur_entry1$M-cur_entry2$M)}) indicates that the verbal plural morpheme does not trigger an illusionary agreement.
%
Accuracy rates for grammatical conditions were nearly equal
(M = \Sexpr{exp2_cur_entry3$M} and \Sexpr{exp2_cur_entry4$M}, 
SE = \Sexpr{exp2_cur_entry3$SE} and \Sexpr{exp2_cur_entry4$SE}, for singular and plural attractors respectively).

@@

@@

 model2_results_table <- fixef(m_responses2, summary = T, robust = F) %>% 
  as.data.frame() #%>% tibble::rownames_to_column("variables")

@@

A Bayesian GLM assuming a Bernoulli distribution with a probit-link function was fit to participants' `acceptable' responses. The model's estimates and 95\% credible intervals are shown in \autoref{fig:exp2ResponseModel}. 
The main effect of \textit{ungrammaticality} (\Sexpr{print_estimate_with_ci( m_responses2, 'cUngrammatical' )}) indicates that, 
on average, participants were quite good at distinguishing between grammatical and ungrammatical sentences. 
Meanwhile, there was no evidence for an interaction between \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses2, 'cUngrammatical:cAttractorPlural')}), indicating 
a similar effect of attractor number in ungrammatical conditions compared to grammatical conditions, and thus no number agreement attraction effect.
Importantly, the negative effect between \textit{the presence of the verbal plural}, \textit{ungrammaticality} and \textit{attractor number} (\Sexpr{print_estimate_with_ci( m_responses2, 'cVerbalAttractor:cUngrammatical:cAttractorPlural')}) indicated that the plural morpheme on the verb of the object relative clause lowered the agreement attraction effects.
